A template for the \emph{arxiv} style

### 2021-08-09 main/main.Rmd
a draft of introduction

Spatio-temporal data

<!-- While satellite imagery can record information on a continuous spatial domain, other spatial information are recorded at a fixed set of locations characterised by latitude, longitude, and other spatial metadata. Examples of this type of data includes climate measures from weather observation stations and river level data recorded by electronic gauges. Analysing this data requires less considerations on the geometry type and map projection while more on how measures in these fixed locations changes across the time domain and whether these changes are related for adjacent locations. -->

Motivation: Many focus on spatio/ temporal solely -> spatio-temporal vector data structure for data analysis

sections

@@

>>>>

Spatio-temporal data record changes of variables [for a reasonable length of period and spread across geographical region]. In this article, we consider spatio-temporal vector data, which are recorded in a fixed interval and are point based, characterised by longitude and latitude, in the spatial aspect. Examples of this type of data include the house price of a city or county, climate measures from weather stations in a country, and river level data from electronic gauges.

Analysing this type of data requires less considerations on the geographical geometry type and map projection but more on how measures in these fixed locations changes across the time domain and whether these changes are related for adjacent locations. For example, when nearby areas show patterns that are regular enough, visualising spatio-temporal data can 1) discover regional time series features, i.e. trend and seasonality, 2) find the Waldo sites from the crowd, and 3) see how correlation of nearby sites changes across time.

The main difficulty in visualising this type of data is to show information in both space and time dimension with the proper level of details without information overflow. This would sometimes require aggregating the time dimension into the proper level or slicing the data into a reasonable number of subset for display. In this sense, a data structure that regulates the manipulation spatio-temporal data will benefit the analysis workflow. While many implementations focus on manipulating and visualising pure spatial or temporal data, there are not sufficient tools to deal with spatio-temporal data. The purpose of this paper is to introduce a spatio-temporal vector data structure for data analysis in R.

The rest of the paper will be divided as follows: Section 2 reviews the existing data structure for spatio, temporal, and spatio-temporal data. Section 3 presents a new data structure for spatio-temporal data: cubble. Then the paper introduces the workflow of data manipulation and visualisation with the cubble structure in Section 4. Section 5 gives some examples on how common spatial and temporal manipulations are performed with cubble and how static and interactive visualisation help to understand climate and [...] data.

@@

# Manipulation and visualisation with `cubble`

Mention different types of manipulation with cubble:

  - `dplyr` support for cubble: 
    - basic 5s: mutate, filter, summarise, select, arrange
    - group and ungroup: group_by, ungroup
    - slice family
  - summarise missing stats

### 2021-08-09 main/main.tex
a draft of introduction

Saptio-temporal data

The rest of the paper will be divided as follows: Section 2 reviews the
existing data structure for spatio, temporal, and spatio-temporal data.
Section 3 presents a new data structure for spatio-temporal data:
cubble. Then the paper introduces the workflow of data manipulation and
visualisation with the cubble structure in Section 4. Section 5 gives
some examples on how common spatial and temporal manipulations are
performed with cubble and how static and interactive visualisation help
ot understand climate and {[}\ldots{]} data.

@@

  \begin{itemize}
  \tightlist
  \item
    basic 5s: mutate, filter, summarise, select, arrange
  \item
    group and ungorup: group\_by, ungroup
  \item
    slice family
  \end{itemize}
\item
  summarise missing stats
\end{itemize}

>>>>

Spatio-temporal data record changes of variables {[}for a reasonable
length of period and spread across geographical region{]}. In this
article, we consider spatio-temporal vector data, which are recorded in
a fixed interval and are point based, characterised by longitude and
latitude, in the spatial aspect. Examples of this type of data include
the house price of a city or county, climate measures from weather
stations in a country, and river level data from electronic gauges.

Analysing this type of data requires less considerations on the
geographical geometry type and map projection but more on how measures
in these fixed locations changes across the time domain and whether
these changes are related for adjacent locations. For example, when
nearby areas show patterns that are regular enough, visualising
spatio-temporal data can 1) discover regional time series features,
i.e.~trend and seasonality, 2) find the Waldo sites from the crowd, and
3) see how correlation of nearby sites changes across time.

The main difficulty in visualising this type of data is to show
information in both space and time dimension with the proper level of
details without information overflow. This would sometimes require
aggregating the time dimension into the proper level or slicing the data
into a reasonable number of subset for display. In this sense, a data
structure that regulates the manipulation spatio-temporal data will
benefit the analysis workflow. While many implementations focus on
manipulating and visualising pure spatial or temporal data, there are
not sufficient tools to deal with spatio-temporal data. The purpose of
this paper is to introduce a spatio-temporal vector data structure for
data analysis in R.

The rest of the paper will be divided as follows: Section 2 reviews the
existing data structure for spatio, temporal, and spatio-temporal data.
Section 3 presents a new data structure for spatio-temporal data:
cubble. Then the paper introduces the workflow of data manipulation and
visualisation with the cubble structure in Section 4. Section 5 gives
some examples on how common spatial and temporal manipulations are
performed with cubble and how static and interactive visualisation help
to understand climate and {[}\ldots{]} data.

@@

  \begin{itemize}
  \tightlist
  \item
    basic 5s: mutate, filter, summarise, select, arrange
  \item
    group and ungroup: group\_by, ungroup
  \item
    slice family
  \end{itemize}
\item
  summarise missing stats
\end{itemize}
